### 2020-05-27 writeup/intro.tex
abstract

>>>>

\begin{abstract}
	We consider multi-task and transfer learning approaches for multiple linear regressions in high dimensions.
	We focus on predicting a particular task to better understand when we should expect multi-task and transfer learning approaches to perform better than using the task alone.
	First, we provide sharp bias-variance tradeoffs for multi-task and transfer learning estimators obtained by solving a commonly used hard parameter sharing architecture.
	Second, we use the technical result to provide more precise interpretations to many empirical phenomena in multi-task and transfer learning.
	For example, we quantify the benefit of multi-task learning for reducing the amount of labeled data, which is a key finding in Taskonomy by Zamir et al.'18.
	Finally, we show practical implications of our theory for detecting and improving negative effects in image and text classification tasks.
	A key technical tool that we develop is the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$ for two random matrices $X_1$ and $X_2$, which may be of independent interest.
\end{abstract}
